% LaTeX resume using res.cls
\documentclass[margin]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\setlength{\textwidth}{5.5 in} % set width of text portion
\addtolength{\topmargin}{-.200in}

\begin{document}

% Center the name over the entire width of resume:
 \moveleft.5\hoffset\centerline{\large\bf Jarrad Battaglia}
% Draw a horizontal line the whole width of resume:
 \moveleft.5\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
% address begins here
% Again, the address lines must be centered over entire width of resume:
 \moveleft.5\hoffset\centerline{285 Third St, Unit 641}
 \moveleft.5\hoffset\centerline{Cambridge, MA 02142}
 \moveleft.5\hoffset\centerline{(610)-420-3083}
 \moveleft.5\hoffset\centerline{jmbbat@gmail.com}
 \moveleft.5\hoffset\centerline{\textbf{Website:}  https://www.linkedin.com/in/jarradbattaglia}

\begin{resume}
 
\section{EDUCATION} {\sl Bachelor of Science,} Computer Science \\
                Drexel University, Philadelphia, PA, June 2014 
  
\section{EXPERIENCE} {\sl Software Engineer} \hfill July 2014 to Present \\
                Amazon.com, Amazon Web Services, Elastic File System \\
                Cambridge, MA 
                 \begin{itemize}  \itemsep -0pt %reduce space between lines
                \item Created Java metering component for the EFS service which tracked customer file system usage and was used for billing purposes.
                \item Designed and implemented a large workload system that could create hundreds of AWS instances to simulate customer-like traffic on dev, gamma, and production instances of the EFS service, which could then scale to the needs of the operator.
                \item Designed and implemented canaries for EFS service that measured different components of customer traffic.
                \item Worked on the EFS deployments team and contributed to adding new functionality to pre-existing deployment library and added concurrent code which decreased time of deployment by two-thirds.
                \item Integrated new internal SSL certificate API into deployment scripts which needed to verify and update EFS server certificates with AWS IAM.
                \item Created deployment scripts for metering EMR code, which deployed from developer desktop or internal CI service into AWS Data Pipeline and S3.
                \end{itemize}
                {\sl Software Engineer Intern} \hfill September 2012 to March 2013 \\
                Amazon.com, Fulfillment By Amazon, Inventory and Reimbursements \\
                Seattle, WA 
                \begin{itemize} \itemsep -0pt
                \item Used AWS Cloudsearch to migrate an internal business site from a SQL database and updated internal website to use new model and service. 
                \item Worked on Reimbursements project which was designed to stop mis-assignments of FBA inventory from being sent to other departments of company.
                \item Created Hadoop EMR job, which measured how many lost items had been mis-assigned in the past 2 years.
                \item Created Integration tests for Reimbursements project.
                \end{itemize}
   
                {\sl Software Engineer Intern} \hfill September 2011 to March 2012 \\
                Unisys, Cloud Computing \\
                Malvern, PA 
                \begin{itemize} \itemsep -0pt
                \item Used Winforms and C Sharp to design and implement a custom XML editing tool that allowed for faster data entry for Cloud Computing team.
                \item Created Perl scripts to add functionality to request tracker ticketing system.
                \item Edited Apache Project Info Reports plugin source code to use IText PDF API to allow plugin to output PDF files.
                \end{itemize}
\section{LANGUAGES AND TOOLS} {\sl\bf Proficient Programming Languages:} Java, Python, Bash \\
                 {\sl\bf Other Programming Languages:} Javascript, C++, Scala \\
                 {\sl\bf Operating Systems:} Ubuntu, Redhat (RHEL 5), Windows \\
                 {\sl\bf Tools \& Frameworks:} AWS Technologies (EC2, IAM, S3, EFS, DynamoDB, EMR), Boto, AWS CLI, AWS SDK (Java), Spring, Akka, Hadoop, Git, Maven, MySQL \\ 

\end{resume}
\end{document}




